A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2016-12-25 twostagedo-rev-Dec-16.tex
made changes to response, and to paper

\section{Experimental Results}
\label{sec:experiments}
\subsection{Scenario}
For the experimental scenario a rectangular block of deformable material, of $8.5 \unit{cm}$ long, $5 \unit{cm}$ wide and $1.8 \unit{cm}$ depth, is placed on a table; the robot pushes the object with a cylindrical finger, followed by a retrieval movement.  A colour firewire camera records the action perpendicularly, while a force sensor registers the reaction forces in synchrony with each photograph taken [\fref{fig:scene}(a)].  \comment{This set up allowed us to study the effect of using an automatically calibrated physics based model as model for the material, while using 2D meshes, even though the same principles can be used if we use a 3D point cloud and a 3D mesh.  To generate the initial mesh for the mass-spring model a routine placed the nodes for the masses evenly spaced on a rectangular grid, given the number of squares we wanted per side.  We made experiments with grids of $3x2, 10x5$ and $20x10$ squares.  To aliviate the bias produced by the springs they were placed in a star pattern, thus compensating forces on eight directions.}

>>>>

\section{Experimental Results}
\label{sec:experiments}
\subsection{Scenario}
For the experimental scenario we used two materials: sponge and plasticine. Each formed a rectangular block of deformable material, of $8.5 \unit{cm}$ long, $5 \unit{cm}$ wide and $1.8 \unit{cm}$ depth. One of the objects is selected, and is placed on a table; the robot pushes the object with a cylindrical finger, followed by a retrieval movement.  A colour firewire camera records the action perpendicularly, while a force sensor registers the reaction forces in synchrony with each photograph taken [\fref{fig:scene}(a)].  \comment{This set up allowed us to study the effect of using an automatically calibrated physics based model as model for the material, while using 2D meshes, even though the same principles can be used if we use a 3D point cloud and a 3D mesh.  To generate the initial mesh for the mass-spring model a routine placed the nodes for the masses evenly spaced on a rectangular grid, given the number of squares we wanted per side.  We made experiments with grids of $3x2, 10x5$ and $20x10$ squares.  To aliviate the bias produced by the springs they were placed in a star pattern, thus compensating forces on eight directions.}
